### 2009-08-07 doc/latex/class_cowichan.tex
Re-generated doxygen with linuxtuples additions.

\includegraphics[height=2cm]{class_cowichan}

@@

Runs the cowichan problem set, chained together. The order in the chain is: \begin{enumerate}
\item \hyperlink{class_cowichan_c44cacf9d9e363a5b076bcee8b9a7a73}{Cowichan::randmat} or \hyperlink{class_cowichan_ec6cc4eb2ad444474b923532167e98a2}{Cowichan::mandel} \item \hyperlink{class_cowichan_308603053675bccbe631f04af921f57c}{Cowichan::half} \item \hyperlink{class_cowichan_ea126792a31e54a8722663b7ea768955}{Cowichan::invperc} or \hyperlink{class_cowichan_a0b633b8c1f21884e0998a9c7020c08c}{Cowichan::thresh} \item \hyperlink{class_cowichan_d449595ef2fe934bdd128ac8b1f51d07}{Cowichan::life} \item \hyperlink{class_cowichan_13d60e06ced3b5da79d62c133ce82337}{Cowichan::winnow} \item \hyperlink{class_cowichan_3df21e3c627958114e045c3559a29f30}{Cowichan::norm} \item \hyperlink{class_cowichan_0c6b68ae3c059b66893405f8530a2e0a}{Cowichan::hull} \item \hyperlink{class_cowichan_52f17221019290b88334b0ca7f3bcdb9}{Cowichan::outer} \item \hyperlink{class_cowichan_aa9aac74b96dc5ed33e821d94649d1b2}{Cowichan::gauss} \item \hyperlink{class_cowichan_92d8d9ae77208115fdfe69e1174f601c}{Cowichan::sor} \item \hyperlink{class_cowichan_3d7d4b581a1d6f0392dc452830fb3b03}{Cowichan::product} (for gauss) \item \hyperlink{class_cowichan_3d7d4b581a1d6f0392dc452830fb3b03}{Cowichan::product} (for sor) \item \hyperlink{class_cowichan_775d72b5e7d122f9f32555352278250e}{Cowichan::vecdiff} \end{enumerate}
\begin{Desc}
\item[Parameters:]
\begin{description}
\item[{\em use\_\-randmat}]in step 1 use: randmat (if true) or mandel (if false). \item[{\em use\_\-thresh}]in step 3 use: thresh (if true) or invperc (if false). \end{description}
\end{Desc}
\hypertarget{class_cowichan_aa9aac74b96dc5ed33e821d94649d1b2}{
\index{Cowichan@{Cowichan}!gauss@{gauss}}
\index{gauss@{gauss}!Cowichan@{Cowichan}}
\subsubsection[{gauss}]{\setlength{\rightskip}{0pt plus 5cm}virtual void Cowichan::gauss ({\bf Matrix} {\em matrix}, \/  {\bf Vector} {\em target}, \/  {\bf Vector} {\em solution})\hspace{0.3cm}{\tt  \mbox{[}protected, pure virtual\mbox{]}}}}
\label{class_cowichan_aa9aac74b96dc5ed33e821d94649d1b2}

@@

Implemented in \hyperlink{class_cowichan_serial_b196d2384c2fe8b185e6269a050399eb}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_363bcd6f0c7b4d0fced94fe4cd59a267}{CowichanOpenMP}, and \hyperlink{class_cowichan_t_b_b_d51868e0e65482f7c9e69d73b3904822}{CowichanTBB}.\hypertarget{class_cowichan_308603053675bccbe631f04af921f57c}{
\index{Cowichan@{Cowichan}!half@{half}}
\index{half@{half}!Cowichan@{Cowichan}}
\subsubsection[{half}]{\setlength{\rightskip}{0pt plus 5cm}virtual void Cowichan::half ({\bf IntMatrix} {\em matrixIn}, \/  {\bf IntMatrix} {\em matrixOut})\hspace{0.3cm}{\tt  \mbox{[}protected, pure virtual\mbox{]}}}}
\label{class_cowichan_308603053675bccbe631f04af921f57c}

@@

Implemented in \hyperlink{class_cowichan_serial_c08a6b3e23ce26959bac12af077f924f}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_70989ffe182aebf590e39c56e146b0fb}{CowichanOpenMP}, and \hyperlink{class_cowichan_t_b_b_bbf17e641657d54fc0c571c008ac8f7a}{CowichanTBB}.\hypertarget{class_cowichan_0c6b68ae3c059b66893405f8530a2e0a}{
\index{Cowichan@{Cowichan}!hull@{hull}}
\index{hull@{hull}!Cowichan@{Cowichan}}
\subsubsection[{hull}]{\setlength{\rightskip}{0pt plus 5cm}virtual void Cowichan::hull ({\bf PointVector} {\em pointsIn}, \/  {\bf PointVector} {\em pointsOut})\hspace{0.3cm}{\tt  \mbox{[}protected, pure virtual\mbox{]}}}}
\label{class_cowichan_0c6b68ae3c059b66893405f8530a2e0a}

@@

Implemented in \hyperlink{class_cowichan_serial_e75cedf0a296dd7ad3dc41cadc51776f}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_cb444dd3e2c0f1f27f4135de0279d09e}{CowichanOpenMP}, and \hyperlink{class_cowichan_t_b_b_0d23aa05dc21fd9e8b033769097b4b18}{CowichanTBB}.\hypertarget{class_cowichan_ea126792a31e54a8722663b7ea768955}{
\index{Cowichan@{Cowichan}!invperc@{invperc}}
\index{invperc@{invperc}!Cowichan@{Cowichan}}
\subsubsection[{invperc}]{\setlength{\rightskip}{0pt plus 5cm}virtual void Cowichan::invperc ({\bf IntMatrix} {\em matrix}, \/  {\bf BoolMatrix} {\em mask})\hspace{0.3cm}{\tt  \mbox{[}protected, pure virtual\mbox{]}}}}
\label{class_cowichan_ea126792a31e54a8722663b7ea768955}

@@

Implemented in \hyperlink{class_cowichan_serial_9b1cf3fcbb40498609826433b8ea2f6a}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_4824c6b8509b5da835fbc5f64eb3e063}{CowichanOpenMP}, and \hyperlink{class_cowichan_t_b_b_e4f9f8c31feea9b3a167fc2880a97610}{CowichanTBB}.\hypertarget{class_cowichan_d449595ef2fe934bdd128ac8b1f51d07}{
\index{Cowichan@{Cowichan}!life@{life}}
\index{life@{life}!Cowichan@{Cowichan}}
\subsubsection[{life}]{\setlength{\rightskip}{0pt plus 5cm}virtual void Cowichan::life ({\bf BoolMatrix} {\em matrixIn}, \/  {\bf BoolMatrix} {\em matrixOut})\hspace{0.3cm}{\tt  \mbox{[}protected, pure virtual\mbox{]}}}}
\label{class_cowichan_d449595ef2fe934bdd128ac8b1f51d07}

@@

Implemented in \hyperlink{class_cowichan_serial_ffd5b022c1d24226e11924094d8af349}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_d24f3ef01289b8f1bd7b864f585daa62}{CowichanOpenMP}, and \hyperlink{class_cowichan_t_b_b_273e3e8a2e05108f59ec613472bfa363}{CowichanTBB}.\hypertarget{class_cowichan_905f3eb45f21cdaa1c32a421d001fa4c}{
\index{Cowichan@{Cowichan}!main@{main}}
\index{main@{main}!Cowichan@{Cowichan}}
\subsubsection[{main}]{\setlength{\rightskip}{0pt plus 5cm}void Cowichan::main (int {\em argc}, \/  char $\ast$ {\em argv}\mbox{[}$\,$\mbox{]}, \/  bool {\em use\_\-randmat}, \/  bool {\em use\_\-thresh})}}
\label{class_cowichan_905f3eb45f21cdaa1c32a421d001fa4c}

@@

Implemented in \hyperlink{class_cowichan_serial_97a58b7901d8a7680cc28d42cb94d532}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_6809c2738792de047ee59259636c1afd}{CowichanOpenMP}, and \hyperlink{class_cowichan_t_b_b_1e58b60ff22a58aba69567ecc6740878}{CowichanTBB}.\hypertarget{class_cowichan_3df21e3c627958114e045c3559a29f30}{
\index{Cowichan@{Cowichan}!norm@{norm}}
\index{norm@{norm}!Cowichan@{Cowichan}}
\subsubsection[{norm}]{\setlength{\rightskip}{0pt plus 5cm}virtual void Cowichan::norm ({\bf PointVector} {\em pointsIn}, \/  {\bf PointVector} {\em pointsOut})\hspace{0.3cm}{\tt  \mbox{[}protected, pure virtual\mbox{]}}}}
\label{class_cowichan_3df21e3c627958114e045c3559a29f30}

@@

Implemented in \hyperlink{class_cowichan_serial_0eeb47447c6a6b94ff7c6999c96fda0e}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_4ffbe36816235bc6abec30eae2be2d78}{CowichanOpenMP}, and \hyperlink{class_cowichan_t_b_b_ca08645b51a242317a115cd7ce7d81fe}{CowichanTBB}.\hypertarget{class_cowichan_52f17221019290b88334b0ca7f3bcdb9}{
\index{Cowichan@{Cowichan}!outer@{outer}}
\index{outer@{outer}!Cowichan@{Cowichan}}
\subsubsection[{outer}]{\setlength{\rightskip}{0pt plus 5cm}virtual void Cowichan::outer ({\bf PointVector} {\em points}, \/  {\bf Matrix} {\em matrix}, \/  {\bf Vector} {\em vector})\hspace{0.3cm}{\tt  \mbox{[}protected, pure virtual\mbox{]}}}}
\label{class_cowichan_52f17221019290b88334b0ca7f3bcdb9}

@@

Implemented in \hyperlink{class_cowichan_serial_05f6899081a457d58978e4f6bda2db6a}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_99a0570f754ac82968d73093476de533}{CowichanOpenMP}, and \hyperlink{class_cowichan_t_b_b_92a763b9733cdcceda13b7b7ea0bc229}{CowichanTBB}.\hypertarget{class_cowichan_14e706ef5a5f7661a623c595d7ed76f1}{
\index{Cowichan@{Cowichan}!print\_\-rect\_\-matrix@{print\_\-rect\_\-matrix}}
\index{print\_\-rect\_\-matrix@{print\_\-rect\_\-matrix}!Cowichan@{Cowichan}}
\subsubsection[{print\_\-rect\_\-matrix}]{\setlength{\rightskip}{0pt plus 5cm}template$<$typename T $>$ void Cowichan::print\_\-rect\_\-matrix (T $\ast$ {\em matrix})\hspace{0.3cm}{\tt  \mbox{[}inline\mbox{]}}}}
\label{class_cowichan_14e706ef5a5f7661a623c595d7ed76f1}

@@

Implemented in \hyperlink{class_cowichan_serial_00411b35445d7d3038b96d53e43bdffa}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_41d0067382570d1e784f62f2c5963d49}{CowichanOpenMP}, and \hyperlink{class_cowichan_t_b_b_f3144458520e2dff1f9fad5753f6fc3d}{CowichanTBB}.\hypertarget{class_cowichan_c44cacf9d9e363a5b076bcee8b9a7a73}{
\index{Cowichan@{Cowichan}!randmat@{randmat}}
\index{randmat@{randmat}!Cowichan@{Cowichan}}
\subsubsection[{randmat}]{\setlength{\rightskip}{0pt plus 5cm}virtual void Cowichan::randmat ({\bf IntMatrix} {\em matrix})\hspace{0.3cm}{\tt  \mbox{[}protected, pure virtual\mbox{]}}}}
\label{class_cowichan_c44cacf9d9e363a5b076bcee8b9a7a73}

@@

Implemented in \hyperlink{class_cowichan_serial_2d24c0e562f7b109ec2ed916f38e5911}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_2c7c4e4dd96f82b7280a412c1fceed2c}{CowichanOpenMP}, and \hyperlink{class_cowichan_t_b_b_b9b5cb4b4b5dc8907b2a01825cd4aaff}{CowichanTBB}.\hypertarget{class_cowichan_92d8d9ae77208115fdfe69e1174f601c}{
\index{Cowichan@{Cowichan}!sor@{sor}}
\index{sor@{sor}!Cowichan@{Cowichan}}
\subsubsection[{sor}]{\setlength{\rightskip}{0pt plus 5cm}virtual void Cowichan::sor ({\bf Matrix} {\em matrix}, \/  {\bf Vector} {\em target}, \/  {\bf Vector} {\em solution})\hspace{0.3cm}{\tt  \mbox{[}protected, pure virtual\mbox{]}}}}
\label{class_cowichan_92d8d9ae77208115fdfe69e1174f601c}

@@

Implemented in \hyperlink{class_cowichan_serial_6e8b06711d976de1adc1e4dc81e560e5}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_d6482d0369a26a51ef0e37ab238fc664}{CowichanOpenMP}, and \hyperlink{class_cowichan_t_b_b_dbb32ce457d0edca6815ab1cb2459276}{CowichanTBB}.\hypertarget{class_cowichan_a0b633b8c1f21884e0998a9c7020c08c}{
\index{Cowichan@{Cowichan}!thresh@{thresh}}
\index{thresh@{thresh}!Cowichan@{Cowichan}}
\subsubsection[{thresh}]{\setlength{\rightskip}{0pt plus 5cm}virtual void Cowichan::thresh ({\bf IntMatrix} {\em matrix}, \/  {\bf BoolMatrix} {\em mask})\hspace{0.3cm}{\tt  \mbox{[}protected, pure virtual\mbox{]}}}}
\label{class_cowichan_a0b633b8c1f21884e0998a9c7020c08c}

@@

Implemented in \hyperlink{class_cowichan_serial_7c0f93b2099ce919f91b5d953ff76511}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_e72c4c0a162f30eac37333bd28db97bc}{CowichanOpenMP}, and \hyperlink{class_cowichan_t_b_b_3306d21f0b3d12cc2e3b050b99812a27}{CowichanTBB}.\hypertarget{class_cowichan_775d72b5e7d122f9f32555352278250e}{
\index{Cowichan@{Cowichan}!vecdiff@{vecdiff}}
\index{vecdiff@{vecdiff}!Cowichan@{Cowichan}}
\subsubsection[{vecdiff}]{\setlength{\rightskip}{0pt plus 5cm}virtual {\bf real} Cowichan::vecdiff ({\bf Vector} {\em actual}, \/  {\bf Vector} {\em computed})\hspace{0.3cm}{\tt  \mbox{[}protected, pure virtual\mbox{]}}}}
\label{class_cowichan_775d72b5e7d122f9f32555352278250e}

@@

Implemented in \hyperlink{class_cowichan_serial_34b75a2084051b3677071bb3c334d1f4}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_92aa23ed47da0a5a3b43416ab08199b3}{CowichanOpenMP}, and \hyperlink{class_cowichan_t_b_b_28c976743df231fd183e4db9306050b1}{CowichanTBB}.\hypertarget{class_cowichan_13d60e06ced3b5da79d62c133ce82337}{
\index{Cowichan@{Cowichan}!winnow@{winnow}}
\index{winnow@{winnow}!Cowichan@{Cowichan}}
\subsubsection[{winnow}]{\setlength{\rightskip}{0pt plus 5cm}virtual void Cowichan::winnow ({\bf IntMatrix} {\em matrix}, \/  {\bf BoolMatrix} {\em mask}, \/  {\bf PointVector} {\em points})\hspace{0.3cm}{\tt  \mbox{[}protected, pure virtual\mbox{]}}}}
\label{class_cowichan_13d60e06ced3b5da79d62c133ce82337}

>>>>

\includegraphics[height=1.56643cm]{class_cowichan}

@@

Runs the cowichan problem set, chained together. The order in the chain is: \begin{enumerate}
\item \hyperlink{class_cowichan_c44cacf9d9e363a5b076bcee8b9a7a73}{Cowichan::randmat} or \hyperlink{class_cowichan_ec6cc4eb2ad444474b923532167e98a2}{Cowichan::mandel} \item \hyperlink{class_cowichan_308603053675bccbe631f04af921f57c}{Cowichan::half} \item \hyperlink{class_cowichan_ea126792a31e54a8722663b7ea768955}{Cowichan::invperc} or \hyperlink{class_cowichan_a0b633b8c1f21884e0998a9c7020c08c}{Cowichan::thresh} \item \hyperlink{class_cowichan_d449595ef2fe934bdd128ac8b1f51d07}{Cowichan::life} \item \hyperlink{class_cowichan_13d60e06ced3b5da79d62c133ce82337}{Cowichan::winnow} \item \hyperlink{class_cowichan_3df21e3c627958114e045c3559a29f30}{Cowichan::norm} \item \hyperlink{class_cowichan_0c6b68ae3c059b66893405f8530a2e0a}{Cowichan::hull} \item \hyperlink{class_cowichan_52f17221019290b88334b0ca7f3bcdb9}{Cowichan::outer} \item \hyperlink{class_cowichan_aa9aac74b96dc5ed33e821d94649d1b2}{Cowichan::gauss} \item \hyperlink{class_cowichan_92d8d9ae77208115fdfe69e1174f601c}{Cowichan::sor} \item \hyperlink{class_cowichan_3d7d4b581a1d6f0392dc452830fb3b03}{Cowichan::product} (for gauss) \item \hyperlink{class_cowichan_3d7d4b581a1d6f0392dc452830fb3b03}{Cowichan::product} (for sor) \item \hyperlink{class_cowichan_775d72b5e7d122f9f32555352278250e}{Cowichan::vecdiff} \end{enumerate}
\begin{Desc}
\item[Parameters:]
\begin{description}
\item[{\em use\_\-randmat}]in step 1 use: randmat (if true) or mandel (if false). \item[{\em use\_\-thresh}]in step 3 use: thresh (if true) or invperc (if false). \end{description}
\end{Desc}

Reimplemented in \hyperlink{class_cowichan_linux_tuples_fd49b2a0af64bafb93a5fe1210c68acd}{CowichanLinuxTuples}.\hypertarget{class_cowichan_aa9aac74b96dc5ed33e821d94649d1b2}{
\index{Cowichan@{Cowichan}!gauss@{gauss}}
\index{gauss@{gauss}!Cowichan@{Cowichan}}
\subsubsection[{gauss}]{\setlength{\rightskip}{0pt plus 5cm}virtual void Cowichan::gauss ({\bf Matrix} {\em matrix}, \/  {\bf Vector} {\em target}, \/  {\bf Vector} {\em solution})\hspace{0.3cm}{\tt  \mbox{[}protected, pure virtual\mbox{]}}}}
\label{class_cowichan_aa9aac74b96dc5ed33e821d94649d1b2}

@@

Implemented in \hyperlink{class_cowichan_serial_b196d2384c2fe8b185e6269a050399eb}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_363bcd6f0c7b4d0fced94fe4cd59a267}{CowichanOpenMP}, \hyperlink{class_cowichan_t_b_b_d51868e0e65482f7c9e69d73b3904822}{CowichanTBB}, \hyperlink{class_cowichan_m_p_i_975f8da6c166fe1db3cf9341eeaab000}{CowichanMPI}, and \hyperlink{class_cowichan_linux_tuples_fd3e659afb38415f56fd508333b7bb1b}{CowichanLinuxTuples}.\hypertarget{class_cowichan_308603053675bccbe631f04af921f57c}{
\index{Cowichan@{Cowichan}!half@{half}}
\index{half@{half}!Cowichan@{Cowichan}}
\subsubsection[{half}]{\setlength{\rightskip}{0pt plus 5cm}virtual void Cowichan::half ({\bf IntMatrix} {\em matrixIn}, \/  {\bf IntMatrix} {\em matrixOut})\hspace{0.3cm}{\tt  \mbox{[}protected, pure virtual\mbox{]}}}}
\label{class_cowichan_308603053675bccbe631f04af921f57c}

@@

Implemented in \hyperlink{class_cowichan_serial_c08a6b3e23ce26959bac12af077f924f}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_70989ffe182aebf590e39c56e146b0fb}{CowichanOpenMP}, \hyperlink{class_cowichan_t_b_b_bbf17e641657d54fc0c571c008ac8f7a}{CowichanTBB}, \hyperlink{class_cowichan_m_p_i_154bbd1a400ee4571f761bff1cdf67cd}{CowichanMPI}, and \hyperlink{class_cowichan_linux_tuples_f3bd58ad2653f06d242d473e7bffda0b}{CowichanLinuxTuples}.\hypertarget{class_cowichan_0c6b68ae3c059b66893405f8530a2e0a}{
\index{Cowichan@{Cowichan}!hull@{hull}}
\index{hull@{hull}!Cowichan@{Cowichan}}
\subsubsection[{hull}]{\setlength{\rightskip}{0pt plus 5cm}virtual void Cowichan::hull ({\bf PointVector} {\em pointsIn}, \/  {\bf PointVector} {\em pointsOut})\hspace{0.3cm}{\tt  \mbox{[}protected, pure virtual\mbox{]}}}}
\label{class_cowichan_0c6b68ae3c059b66893405f8530a2e0a}

@@

Implemented in \hyperlink{class_cowichan_serial_e75cedf0a296dd7ad3dc41cadc51776f}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_cb444dd3e2c0f1f27f4135de0279d09e}{CowichanOpenMP}, \hyperlink{class_cowichan_t_b_b_0d23aa05dc21fd9e8b033769097b4b18}{CowichanTBB}, \hyperlink{class_cowichan_m_p_i_22b3dce35fd93635bd4c1596e7fb839c}{CowichanMPI}, and \hyperlink{class_cowichan_linux_tuples_501f87594d62af261ff0b1954a60ddc4}{CowichanLinuxTuples}.\hypertarget{class_cowichan_ea126792a31e54a8722663b7ea768955}{
\index{Cowichan@{Cowichan}!invperc@{invperc}}
\index{invperc@{invperc}!Cowichan@{Cowichan}}
\subsubsection[{invperc}]{\setlength{\rightskip}{0pt plus 5cm}virtual void Cowichan::invperc ({\bf IntMatrix} {\em matrix}, \/  {\bf BoolMatrix} {\em mask})\hspace{0.3cm}{\tt  \mbox{[}protected, pure virtual\mbox{]}}}}
\label{class_cowichan_ea126792a31e54a8722663b7ea768955}

@@

Implemented in \hyperlink{class_cowichan_serial_9b1cf3fcbb40498609826433b8ea2f6a}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_4824c6b8509b5da835fbc5f64eb3e063}{CowichanOpenMP}, \hyperlink{class_cowichan_t_b_b_e4f9f8c31feea9b3a167fc2880a97610}{CowichanTBB}, \hyperlink{class_cowichan_m_p_i_bcd0f18fcccc8973ddaacf4dda190b53}{CowichanMPI}, and \hyperlink{class_cowichan_linux_tuples_5497a17a63cc5faad7afa54d013ea741}{CowichanLinuxTuples}.\hypertarget{class_cowichan_d449595ef2fe934bdd128ac8b1f51d07}{
\index{Cowichan@{Cowichan}!life@{life}}
\index{life@{life}!Cowichan@{Cowichan}}
\subsubsection[{life}]{\setlength{\rightskip}{0pt plus 5cm}virtual void Cowichan::life ({\bf BoolMatrix} {\em matrixIn}, \/  {\bf BoolMatrix} {\em matrixOut})\hspace{0.3cm}{\tt  \mbox{[}protected, pure virtual\mbox{]}}}}
\label{class_cowichan_d449595ef2fe934bdd128ac8b1f51d07}

@@

Implemented in \hyperlink{class_cowichan_serial_ffd5b022c1d24226e11924094d8af349}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_d24f3ef01289b8f1bd7b864f585daa62}{CowichanOpenMP}, \hyperlink{class_cowichan_t_b_b_273e3e8a2e05108f59ec613472bfa363}{CowichanTBB}, \hyperlink{class_cowichan_m_p_i_9c739951d036ef7905bda7cb896e0edf}{CowichanMPI}, and \hyperlink{class_cowichan_linux_tuples_967138bbdead76eec50f31465dd9d5f1}{CowichanLinuxTuples}.\hypertarget{class_cowichan_905f3eb45f21cdaa1c32a421d001fa4c}{
\index{Cowichan@{Cowichan}!main@{main}}
\index{main@{main}!Cowichan@{Cowichan}}
\subsubsection[{main}]{\setlength{\rightskip}{0pt plus 5cm}void Cowichan::main (int {\em argc}, \/  char $\ast$ {\em argv}\mbox{[}$\,$\mbox{]}, \/  bool {\em use\_\-randmat}, \/  bool {\em use\_\-thresh})}}
\label{class_cowichan_905f3eb45f21cdaa1c32a421d001fa4c}

@@

Implemented in \hyperlink{class_cowichan_serial_97a58b7901d8a7680cc28d42cb94d532}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_6809c2738792de047ee59259636c1afd}{CowichanOpenMP}, \hyperlink{class_cowichan_t_b_b_1e58b60ff22a58aba69567ecc6740878}{CowichanTBB}, \hyperlink{class_cowichan_m_p_i_58274fc55ed8a352a8924b130f3b5d2e}{CowichanMPI}, and \hyperlink{class_cowichan_linux_tuples_8774404842868381379ec627e8373cec}{CowichanLinuxTuples}.\hypertarget{class_cowichan_3df21e3c627958114e045c3559a29f30}{
\index{Cowichan@{Cowichan}!norm@{norm}}
\index{norm@{norm}!Cowichan@{Cowichan}}
\subsubsection[{norm}]{\setlength{\rightskip}{0pt plus 5cm}virtual void Cowichan::norm ({\bf PointVector} {\em pointsIn}, \/  {\bf PointVector} {\em pointsOut})\hspace{0.3cm}{\tt  \mbox{[}protected, pure virtual\mbox{]}}}}
\label{class_cowichan_3df21e3c627958114e045c3559a29f30}

@@

Implemented in \hyperlink{class_cowichan_serial_0eeb47447c6a6b94ff7c6999c96fda0e}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_4ffbe36816235bc6abec30eae2be2d78}{CowichanOpenMP}, \hyperlink{class_cowichan_t_b_b_ca08645b51a242317a115cd7ce7d81fe}{CowichanTBB}, \hyperlink{class_cowichan_m_p_i_11df49e804427d4a0d085f4cff9302d0}{CowichanMPI}, and \hyperlink{class_cowichan_linux_tuples_922209c219bb5b9268263dae4000ea81}{CowichanLinuxTuples}.\hypertarget{class_cowichan_52f17221019290b88334b0ca7f3bcdb9}{
\index{Cowichan@{Cowichan}!outer@{outer}}
\index{outer@{outer}!Cowichan@{Cowichan}}
\subsubsection[{outer}]{\setlength{\rightskip}{0pt plus 5cm}virtual void Cowichan::outer ({\bf PointVector} {\em points}, \/  {\bf Matrix} {\em matrix}, \/  {\bf Vector} {\em vector})\hspace{0.3cm}{\tt  \mbox{[}protected, pure virtual\mbox{]}}}}
\label{class_cowichan_52f17221019290b88334b0ca7f3bcdb9}

@@

Implemented in \hyperlink{class_cowichan_serial_05f6899081a457d58978e4f6bda2db6a}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_99a0570f754ac82968d73093476de533}{CowichanOpenMP}, \hyperlink{class_cowichan_t_b_b_92a763b9733cdcceda13b7b7ea0bc229}{CowichanTBB}, \hyperlink{class_cowichan_m_p_i_39fcc8a331b0e26438fbf43fa01cf7c1}{CowichanMPI}, and \hyperlink{class_cowichan_linux_tuples_b16e1c3b60f920c12460a74289558dcb}{CowichanLinuxTuples}.\hypertarget{class_cowichan_14e706ef5a5f7661a623c595d7ed76f1}{
\index{Cowichan@{Cowichan}!print\_\-rect\_\-matrix@{print\_\-rect\_\-matrix}}
\index{print\_\-rect\_\-matrix@{print\_\-rect\_\-matrix}!Cowichan@{Cowichan}}
\subsubsection[{print\_\-rect\_\-matrix}]{\setlength{\rightskip}{0pt plus 5cm}template$<$typename T $>$ void Cowichan::print\_\-rect\_\-matrix (T $\ast$ {\em matrix})\hspace{0.3cm}{\tt  \mbox{[}inline\mbox{]}}}}
\label{class_cowichan_14e706ef5a5f7661a623c595d7ed76f1}

@@

Implemented in \hyperlink{class_cowichan_serial_00411b35445d7d3038b96d53e43bdffa}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_41d0067382570d1e784f62f2c5963d49}{CowichanOpenMP}, \hyperlink{class_cowichan_t_b_b_f3144458520e2dff1f9fad5753f6fc3d}{CowichanTBB}, \hyperlink{class_cowichan_m_p_i_1b7dccf774caccb26839cd29fe0a5cb0}{CowichanMPI}, and \hyperlink{class_cowichan_linux_tuples_c4874f09c54056ac94d00f9e341a94f4}{CowichanLinuxTuples}.\hypertarget{class_cowichan_c44cacf9d9e363a5b076bcee8b9a7a73}{
\index{Cowichan@{Cowichan}!randmat@{randmat}}
\index{randmat@{randmat}!Cowichan@{Cowichan}}
\subsubsection[{randmat}]{\setlength{\rightskip}{0pt plus 5cm}virtual void Cowichan::randmat ({\bf IntMatrix} {\em matrix})\hspace{0.3cm}{\tt  \mbox{[}protected, pure virtual\mbox{]}}}}
\label{class_cowichan_c44cacf9d9e363a5b076bcee8b9a7a73}

@@

Implemented in \hyperlink{class_cowichan_serial_2d24c0e562f7b109ec2ed916f38e5911}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_2c7c4e4dd96f82b7280a412c1fceed2c}{CowichanOpenMP}, \hyperlink{class_cowichan_t_b_b_b9b5cb4b4b5dc8907b2a01825cd4aaff}{CowichanTBB}, \hyperlink{class_cowichan_m_p_i_6805f21144aeaeddc4549e1b2b42bca8}{CowichanMPI}, and \hyperlink{class_cowichan_linux_tuples_ff90c6a27db51366570b70d352de7fab}{CowichanLinuxTuples}.\hypertarget{class_cowichan_92d8d9ae77208115fdfe69e1174f601c}{
\index{Cowichan@{Cowichan}!sor@{sor}}
\index{sor@{sor}!Cowichan@{Cowichan}}
\subsubsection[{sor}]{\setlength{\rightskip}{0pt plus 5cm}virtual void Cowichan::sor ({\bf Matrix} {\em matrix}, \/  {\bf Vector} {\em target}, \/  {\bf Vector} {\em solution})\hspace{0.3cm}{\tt  \mbox{[}protected, pure virtual\mbox{]}}}}
\label{class_cowichan_92d8d9ae77208115fdfe69e1174f601c}

@@

Implemented in \hyperlink{class_cowichan_serial_6e8b06711d976de1adc1e4dc81e560e5}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_d6482d0369a26a51ef0e37ab238fc664}{CowichanOpenMP}, \hyperlink{class_cowichan_t_b_b_dbb32ce457d0edca6815ab1cb2459276}{CowichanTBB}, \hyperlink{class_cowichan_m_p_i_7388c844e8aa73ab0923443a3a7ef069}{CowichanMPI}, and \hyperlink{class_cowichan_linux_tuples_aa2c469c3f520a5a56c5ec1ac9a5a6c6}{CowichanLinuxTuples}.\hypertarget{class_cowichan_a0b633b8c1f21884e0998a9c7020c08c}{
\index{Cowichan@{Cowichan}!thresh@{thresh}}
\index{thresh@{thresh}!Cowichan@{Cowichan}}
\subsubsection[{thresh}]{\setlength{\rightskip}{0pt plus 5cm}virtual void Cowichan::thresh ({\bf IntMatrix} {\em matrix}, \/  {\bf BoolMatrix} {\em mask})\hspace{0.3cm}{\tt  \mbox{[}protected, pure virtual\mbox{]}}}}
\label{class_cowichan_a0b633b8c1f21884e0998a9c7020c08c}

@@

Implemented in \hyperlink{class_cowichan_serial_7c0f93b2099ce919f91b5d953ff76511}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_e72c4c0a162f30eac37333bd28db97bc}{CowichanOpenMP}, \hyperlink{class_cowichan_t_b_b_3306d21f0b3d12cc2e3b050b99812a27}{CowichanTBB}, \hyperlink{class_cowichan_m_p_i_49ff96b091a61e9cfd9aad8824e7fbbd}{CowichanMPI}, and \hyperlink{class_cowichan_linux_tuples_b8cf055ec3d42a1ccde6d818c5a43a74}{CowichanLinuxTuples}.\hypertarget{class_cowichan_775d72b5e7d122f9f32555352278250e}{
\index{Cowichan@{Cowichan}!vecdiff@{vecdiff}}
\index{vecdiff@{vecdiff}!Cowichan@{Cowichan}}
\subsubsection[{vecdiff}]{\setlength{\rightskip}{0pt plus 5cm}virtual {\bf real} Cowichan::vecdiff ({\bf Vector} {\em actual}, \/  {\bf Vector} {\em computed})\hspace{0.3cm}{\tt  \mbox{[}protected, pure virtual\mbox{]}}}}
\label{class_cowichan_775d72b5e7d122f9f32555352278250e}

@@

Implemented in \hyperlink{class_cowichan_serial_34b75a2084051b3677071bb3c334d1f4}{CowichanSerial}, \hyperlink{class_cowichan_open_m_p_92aa23ed47da0a5a3b43416ab08199b3}{CowichanOpenMP}, \hyperlink{class_cowichan_t_b_b_28c976743df231fd183e4db9306050b1}{CowichanTBB}, \hyperlink{class_cowichan_m_p_i_c5470a2876efecf843b19c37c21ecf19}{CowichanMPI}, and \hyperlink{class_cowichan_linux_tuples_213185666ea7dd0c9abc59899b454086}{CowichanLinuxTuples}.\hypertarget{class_cowichan_13d60e06ced3b5da79d62c133ce82337}{
\index{Cowichan@{Cowichan}!winnow@{winnow}}
\index{winnow@{winnow}!Cowichan@{Cowichan}}
\subsubsection[{winnow}]{\setlength{\rightskip}{0pt plus 5cm}virtual void Cowichan::winnow ({\bf IntMatrix} {\em matrix}, \/  {\bf BoolMatrix} {\em mask}, \/  {\bf PointVector} {\em points})\hspace{0.3cm}{\tt  \mbox{[}protected, pure virtual\mbox{]}}}}
\label{class_cowichan_13d60e06ced3b5da79d62c133ce82337}
